\section{FORMAT Control the Format of Matrix Display}

\subsection{Usage}

FreeMat supports several modes for displaying matrices (either through the
\verb|disp| function or simply by entering expressions on the command line.  
There are several options for the format command.  The default mode is equivalent
to
\begin{verbatim}
   format short
\end{verbatim}
which generally displays matrices with 4 decimals, and scales matrices if the entries
have magnitudes larger than roughly \verb|1e2| or smaller than \verb|1e-2|.   For more 
information you can use 
\begin{verbatim}
   format long
\end{verbatim}
which displays roughly 7 decimals for \verb|float| and \verb|complex| arrays, and 14 decimals
for \verb|double| and \verb|dcomplex|.  You can also use
\begin{verbatim}
   format short e
\end{verbatim}
to get exponential format with 4 decimals.  Matrices are not scaled for exponential 
formats.  Similarly, you can use
\begin{verbatim}
   format long e
\end{verbatim}
which displays the same decimals as \verb|format long|, but in exponential format.
You can also use the \verb|format| command to retrieve the current format:
\begin{verbatim}
   s = format
\end{verbatim}
where \verb|s| is a string describing the current format.
\subsection{Example}

We start with the short format, and two matrices, one of double precision, and the
other of single precision.
@>
Note that in the short format, these two matrices are displayed with the same format.
In \verb|long| format, however, they display differently
@>
Note also that we we scale the contents of the matrices, FreeMat rescales the entries
with a scale premultiplier.
@>
Next, we use the exponential formats:
@>
Finally, if we assign the \verb|format| function to a variable, we can retrieve the 
current format:
@>
